### 2017-07-07 paper.tex
Formatting fixes to get it through arxiv.org

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

@@

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

The best way to choose tools for managing lessons is
to ask potential contributors what they are comfortable with
rather than requiring \emph{them} to come to \emph{you}.
Remember also that contributing to a lesson is probably not their top priority,
and look for ways to reduce their cognitive load.
For example,
threaded discussion forums can improve the signal-to-noise ratio
by reducing long reply-all email exchanges.
Several open frameworks are available to facilitate development of new lessons,
such as learnr (\url{https://rstudio.github.io/learnr}),
Morea (\url{https://morea-framework.github.io}),
and DataCamp's templates (\url{https://www.datacamp.com/teach/documentation}).

@@

Academia has only a few ways of recognizing contributions.
Until these are expanded,
it is important to publish lessons in ways that traditional academic systems can digest.
One is to give releases DOIs supplied by providers such as Zenodo (\url{https://zenodo.org/})
or DataCite (\url{https://www.datacite.org/}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to differentiate recognition of their contributions.
Each time the lesson is published,
names (and identifiers such as ORCIDs (\url{https://orcid.org}))
should be gathered for all contributors.

@@

Before re-using content,
make sure to check its license.
Both Programming Historian and the Carpentry projects
use the Creative Commons--Attribution license
(\url{https://creativecommons.org/licenses/by/4.0/}),
which allows people to share and adapt material for any purpose
as long as they cite the original source.
Other Creative Commons licenses may restrict commercial use
and/or creation of derivative materials.

@@

\bibitem{instructor-training}
Koch C. and Wilson G. (eds.)
\newblock Software Carpentry: Instructor Training; 2016.
\newblock \url{https://zenodo.org/record/57571#.WS8huDOZPdQ}.

@@

\bibitem{shell2015}
Devenyi G.~A. and Koch C. (eds.):
Software Carpentry: The Unix Shell; 2015.
\newblock \url{https://zenodo.org/record/27355#.WS8lajOZPdQ}.

\bibitem{shell2017}
Devenyi G.~A. and Srinath A. (eds.):
Software Carpentry: The Unix Shell; 2017.
\newblock \url{https://zenodo.org/record/278226#.WS74tTOZPdQ}.

\bibitem{choral-explanations}
Caulfield M. Choral Explanations; 2016.
\newblock \url{https://hapgood.us/2016/05/13/choral-explanations/}.

@@

\bibitem{git-survey}
GitLab
\newblock Global Developer Survey.
\newblock \url{http://get.gitlab.com/global-developer-survey/}, 2016.

>>>>

% Use nameref to cite supporting information files (see Supporting Information section for more info)
% \usepackage{nameref,hyperref}

@@

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
% \lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
% \lfoot{\sf PLOS}

@@

The best way to choose tools for managing lessons is
to ask potential contributors what they are comfortable with
rather than requiring \emph{them} to come to \emph{you}.
Remember also that contributing to a lesson is probably not their top priority,
and look for ways to reduce their cognitive load.
For example,
threaded discussion forums can improve the signal-to-noise ratio
by reducing long reply-all email exchanges.
Several open frameworks are available to facilitate development of new lessons,
such as learnr (\texttt{https://rstudio.github.io/learnr}),
Morea (\texttt{https://morea-framework.github.io}),
and DataCamp's templates (\texttt{https://www.datacamp.com/teach/documentation}).

@@

Academia has only a few ways of recognizing contributions.
Until these are expanded,
it is important to publish lessons in ways that traditional academic systems can digest.
One is to give releases DOIs supplied by providers such as Zenodo (\texttt{https://zenodo.org/})
or DataCite (\texttt{https://www.datacite.org/}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to differentiate recognition of their contributions.
Each time the lesson is published,
names (and identifiers such as ORCIDs (\texttt{https://orcid.org}))
should be gathered for all contributors.

@@

Before re-using content,
make sure to check its license.
Both Programming Historian and the Carpentry projects
use the Creative Commons--Attribution license
(\texttt{https://creativecommons.org/licenses/by/4.0/}),
which allows people to share and adapt material for any purpose
as long as they cite the original source.
Other Creative Commons licenses may restrict commercial use
and/or creation of derivative materials.

@@

\bibitem{instructor-training}
Koch C. and Wilson G. (eds.)
\newblock Software Carpentry: Instructor Training; 2016.
\newblock \texttt{https://zenodo.org/record/57571\#.WS8huDOZPdQ}.

@@

\bibitem{shell2015}
Devenyi G.~A. and Koch C. (eds.):
Software Carpentry: The Unix Shell; 2015.
\newblock \texttt{https://zenodo.org/record/27355\#.WS8lajOZPdQ}.

\bibitem{shell2017}
Devenyi G.~A. and Srinath A. (eds.):
Software Carpentry: The Unix Shell; 2017.
\newblock \texttt{https://zenodo.org/record/278226\#.WS74tTOZPdQ}.

\bibitem{choral-explanations}
Caulfield M. Choral Explanations; 2016.
\newblock \texttt{https://hapgood.us/2016/05/13/choral-explanations/}.

@@

\bibitem{git-survey}
GitLab
\newblock Global Developer Survey.
\newblock \texttt{http://get.gitlab.com/global-developer-survey/}, 2016.
